---
title: "SURVEY TITLE"
author: 'AUTHOR'
subtitle: "ADD SURVEY DETAILS - STUDY LOCATION, STUDY PERIOD, ETC"
---
 
Recommended citation:

## Report template with results from WHO Anthro Survey Analyser

Analysis date: `r Sys.time()`

Link: https://whonutrition.shinyapps.io/anthro/

```{r setup, cache=FALSE, message=FALSE, echo=FALSE, warning=FALSE, results='hide'}
knitr::opts_chunk$set(cache=FALSE, message=FALSE, echo=FALSE, warning=FALSE, results='asis', fig.height=3)
options(knitr.kable.NA = '')

caption <- captioner::captioner()
# Create stratification variables for use in automated reporting
other_grouping_name <- anthro_make_grouping_label(list_map_vars[['othergr']]())
df_strat <-
  tibble(
   key = c('Age group', 'Sex', 'Residence type', 'Geographical region', 'Wealth quintile', 'Mother education', other_grouping_name),
    value = c('age_group', list_map_vars[['sex']](), list_map_vars[['typeres']](), list_map_vars[['gregion']](), list_map_vars[['wealthq']](), list_map_vars[['mothered']](), list_map_vars[['othergr']]())
  ) %>%
  filter(!value %in% 'None')

inc_progress()

# check that all list_map_vars are part of the dataset
# as list_map_vars are user supplied
stopifnot(all(df_strat$value %in% colnames(df_filtered())))

df_zscores <-
  CalculateZScores(
    data = df_filtered(),
    sex = list_map_vars[['sex']](),
    weight = list_map_vars[['weight']](),
    lenhei = list_map_vars[['lenhei']](),
    lenhei_unit = list_map_vars[['lenhei_unit']](),
    oedema = list_map_vars[['oedema']]()
  )

inc_progress()

# calculate the missing cases if cluster, strata or sw is set
prev_missing_vals <- anthro_prev_excluded_cases(df_zscores, list_map_vars)
prev_missing_values_names <- prev_missing_vals$missing_values_names
prev_missing_value_counts <- prev_missing_vals$missing_value_counts
    
df_prevs <-
  CalculatePrev(
    data = df_zscores,
    age.month = age_in_months(), age = list_map_vars[['age']](),
    date_birth = list_map_vars[['date_birth']](), date_obs = list_map_vars[['date_obs']](),
    sex = list_map_vars[['sex']](),
    weight = list_map_vars[['weight']](), lenhei = list_map_vars[['lenhei']](),
    lenhei_unit = list_map_vars[['lenhei_unit']](), sw = list_map_vars[['sw']](),
    cluster = list_map_vars[['cluster']](), strata = list_map_vars[['strata']](),
    typeres = list_map_vars[['typeres']](), gregion = list_map_vars[['gregion']](),
    wealthq = list_map_vars[['wealthq']](), mothered = list_map_vars[['mothered']](),
    othergr = list_map_vars[['othergr']](), 
    oedema = list_map_vars[['oedema']]()
  )

```

# Overall survey results summary

## Outcome plots

```{r, fig.pos='!htbp', fig.fullwidth = TRUE, fig.cap='Nutritional status by stratification variable' %>% caption('a', .), fig.height=8, fig.width=12, fig.align='center', out.extra='angle=270', dpi=600}
inc_progress()
name_var <-
  str_c(rep(c("Stunting", "Wasting", 'Severe wasting', "Overweight", 'Obesity', "Underweight"), each = 3), c('_r', '_ll', '_ul'))

select_var <-
  c(
    str_c(
      rep('HA_2', each = 3),
      c('_r', '_ll', '_ul')
    ),
    str_c(
      rep('WH', each = 3),
      rep(c('_2', '_3'), each = 3),
      c('_r', '_ll', '_ul')
    ),
    str_c(
      rep('WH', each = 3),
      rep(c('2', '3'), each = 3),
      c('_r', '_ll', '_ul')
    ),
    str_c(
      rep('WA_2', each = 3),
      c('_r', '_ll', '_ul')
    )
  )

tmp <-
  df_prevs %>% 
  filter(str_detect(Group, c('All|Age group|Sex|Area|Wealth quintile'))) %>%
  select(Group, one_of(select_var)) %>%
  set_names(c('key', name_var)) %>% 
  gather(outcome, prop, -key) %>% 
  mutate(
    prop = prop %>% as.numeric(),
    key = key %>% fct_inorder(),
    z = str_replace_all(outcome, c('.*_r' = 'estimate', '.*_ll' = 'lower', '.*_ul' = 'upper')),
    outcome = str_replace_all(outcome, '_.*', '') %>% fct_inorder()
  ) %>% 
  spread(key = z, value = prop)

p <- 
  tmp %>% 
  filter(!str_detect(key, 'All')) %>% 
  full_join(tmp %>% filter(str_detect(key, 'All')) %>% select(-key), by = 'outcome') %>% 
  filter(outcome != 'Obesity') %>%  # exclude obesity in plot
  mutate(legend = 'Total /n (95% CI)') %>% 
  ggplot() +
  aes(x = key %>% fct_rev) +
  geom_pointrange(aes(y = estimate.x, ymin = lower.x, ymax = upper.x), fatten = 2) +
  geom_hline(aes(yintercept = estimate.y, colour = 'Total \n (95% CI)'), alpha = .5, linetype = 'dashed') +
  geom_ribbon(aes(ymin = lower.y, ymax = upper.y, fill = 'Total \n (95% CI)'), group = 1, alpha = .25) +
  scale_colour_manual('', breaks = c("Total (95% CI)"), values = c("black")) +
  scale_fill_manual('', breaks = c("Total (95% CI)"), values = c("grey75")) +
  guides(colour = guide_legend(nrow = 2)) +
  coord_flip() +
  expand_limits(y = 0) +
  labs(x = '', y = 'Proportion (%)') +
  facet_grid(~ outcome, scales = 'free') +
  hrbrthemes::theme_ipsum(grid = 'XY', base_family = 'Palatino', base_size = 9, axis_title_size = 10, axis_title_face = 'bold', strip_text_size = 11, strip_text_face = 'bold') +
  theme(legend.position = 'bottom')

p %>% print
```

\clearpage

# Summary on survey description

```{r calculations}
inc_progress()
data_collect_start <-
  if(list_map_vars[['date_obs']]() != 'None') {
    tmp <- df_zscores[[list_map_vars[['date_obs']]()]] %>% min(na.rm = TRUE)
    str_c(day(tmp), month(tmp, label = TRUE), year(tmp), sep = ' ')
  } else {
    'unknown'
  }

data_collect_end <-
  if(list_map_vars[['date_obs']]() != 'None') {
    tmp <- df_zscores[[list_map_vars[['date_obs']]()]] %>% max(na.rm = TRUE)
    str_c(day(tmp), month(tmp, label = TRUE), year(tmp), sep = ' ')
  } else {
    'unknown'
  }

# Raw numbers
df_eligible <- df_zscores
eligible_total <- df_eligible %>% nrow()
eligible_height <- 
  df_eligible %>% filter_(interp(~ x > 0, x = as.name(list_map_vars[['lenhei']]()))) %>% nrow()
eligible_weight <- 
  df_eligible %>% filter_(interp(~ x > 0, x = as.name(list_map_vars[['weight']]()))) %>% nrow()
eligible_height_text <- str_c(eligible_height, ' (', (eligible_height/eligible_total*100) %>% round(1), '%)')
eligible_weight_text <- str_c(eligible_weight, ' (', (eligible_weight/eligible_total*100) %>% round(1), '%)')

# Oedema
oedema_n <- 
  ifelse(
    list_map_vars[['oedema']]() == 'None', 'None', 
    df_zscores %>% 
      group_by_(list_map_vars[['oedema']]()) %>% 
      tally %>% 
      filter_(
        interp(
          ~ x %in% c('Y', 'y', '1', 1), 
          x = as.name(list_map_vars[['oedema']]())
        )
      ) %>% 
      extract2('n')
  )

is_oedema_mapped <- !is.na(oedema_n) && length(oedema_n) == 1L && oedema_n > 0 && oedema_n != "None"

# helper function for later in the document
print_oedema_note <- function(oedema_n) {
  if (is_oedema_mapped && oedema_n > 0) {
    cat("\nThere were ", oedema_n, " cases of bilateral oedema, for which weight-for-age and weight-for-height z-scores were considered as below -3 for prevalence calculation purposes.\n")
  }
}

oedema_sentence <- 
  ifelse(oedema_n == 'None', 'Information on oedema was not provided.', 
         str_c('There were', oedema_n, 'cases of oedema reported.', sep = ' '))

# Flags
flag_available <- zscore_flag_cols

flag_n <-
  df_zscores %>%
  summarise_at(vars(one_of(flag_available)), funs(sum(!is.na(.)))) %>%
  gather(key, N)

flag_sum <-
  df_zscores %>%
  summarise_at(vars(one_of(flag_available)), funs(sum(., na.rm = TRUE))) %>%
  gather(key, n)

df_flag <-
  full_join(flag_n, flag_sum) %>%
  mutate(
    pretty_key = fct_recode(key, `length- or height-for-age` = 'zlen_flag', `weight-for-length or height` = 'zwfl_flag', `weight-for-age` = 'zwei_flag', `body mass index-for-age` = 'zbmi_flag') %>% as.character(),
    prop = (n/N*100) %>% round(1)
  )

flag_sentence <-
  str_c(
    'There were ',
    df_flag %>%
      select(-key, -N) %>%
      as.list %>%
      pmap(function(pretty_key, n, prop) str_c(n, ' (', prop, '%) ', 'flags for ', pretty_key, sep = '')) %>%
      str_c(collapse = ', '),
    '.'
  )

# missing age
# the missing age is computed by looking at the zscore age column
# and relating that to the total number of records of the z_scores
stopifnot('age_in_days' %in% colnames(df_zscores))
ages <- as.numeric(df_filtered()[['age_in_days']])
missing_age_n <- sum(is.na(ages))
n_rows <- nrow(df_filtered())
percent_format <- function(value) format(round(value / n_rows * 100, 1), digits = 1)
missing_age_text <- paste0(if (missing_age_n == 1) 'was ' else 'were ',
                           missing_age_n, ' (',
                           percent_format(missing_age_n),
                           '%) ',
                           if (missing_age_n == 1) 'child' else 'children')
no_negative_age <- sum(df_filtered()[['age_in_days']] < 0, na.rm = TRUE)
negative_age_text <- if (no_negative_age > 0) {
  paste0(" and ", no_negative_age,
         " (" , percent_format(no_negative_age), "%) ",
         if (no_negative_age == 1) "child" else "children", " with negative values for age")
} else {
  ""
}

sex_col <- list_map_vars[['sex']]()
missing_sex_n <- sum(is.na(df_filtered()[[sex_col]]))
missing_sex_text <- paste0(
  if (missing_age_n == 1) 'was ' else 'were ',
  missing_sex_n, ' (',
  percent_format(missing_sex_n),
  '%) ', ' ',
  if (missing_age_n == 1) 'child' else 'children'
)

removed_due_to_age_text <- ""
if (number_removed_due_to_age() > 0) {
  n <- number_removed_due_to_age()
  n_percent <- percent_format(n)
  was <- if (n == 1) "was " else "were "
  children <- if (n == 1) "child " else "children "
  removed_due_to_age_text <- paste0(
    "There ", was, " ", n,
    " (", n_percent, "%) ", children,
    " aged greater than sixty months who ", was,
    " excluded from the analysis."
  )
}
```

## Sample size:
The original sample was of `r nrow(df_raw())` children. There were `r eligible_total` children retained after filtering for [**INSERT DETAILS OF ANY FILTERING APPLIED**]; height measurements were obtained for `r eligible_height_text` children and weight measurements were obtained for `r eligible_weight_text`. There `r missing_sex_text` with missing information on sex and there `r missing_age_text` with missing age`r negative_age_text`.
`r removed_due_to_age_text`
`r oedema_sentence`

```{r, echo = FALSE, results = 'asis'}
walk2(prev_missing_values_names, prev_missing_value_counts, function(col, count) {
  if (count > 0) {
    cat('\\n')
    child <- if (count == 1) "child" else "children"
    was <- if (count == 1) "was" else "were"
    cat(count, " ", child," had missing '", col,"' information and ", was," excluded from the prevalence calculations.")
    cat('\\n')
  }
})
```

## Sample design:

## Household listing (source or how was it done to update existing information)

## Training of field staff: How many, how many teams, how many measurements per team per day

## Standardization

## Equipment and calibration

## Data collection period

Data collection: Start: [**enter month and year the survey started MM/YYYY**]; End: [**enter month and year the survey ended MM/YYYY**]

## Data entry

## Supervision

# Other survey context important for the interpretation of results
## Seasonality (e.g. harvest and malaria)
## Climate conditions (e.g. monsoon, drought, natural catastrophes)
## Epidemics, high mortality
## Security issues, civil unrest
## Population groups not covered (e.g. slums, refugees)

# Summary of survey analysis
## Data processing: Software …..

## Data cleaning:
## Imputations:

# Data quality indicators and assessment
## Flags:

Flags were calculated as follows:...

`r flag_sentence`

## Missing data
```{r missing_data, fig.cap="Missing data" %>% caption('b', .), fig.pos='!htbp', fig.fullwidth = F, fig.height=2.5, dpi=600}
inc_progress()
quality_vars <-
  tibble(
    key = c('Age', 'Weight (kg)', 'Length or height (cm)'), 
    value = c('age_in_days', list_map_vars[['weight']](), list_map_vars[['lenhei']]())
  ) %>%
  bind_rows(df_strat) %>%
  mutate(
    key = fct_inorder(key)
  ) %>%
  filter(!value %in% c('None', 'age_group'))
df_missing <-
  df_zscores %>%
  select(one_of(quality_vars$value)) %>%
  mutate_all(funs(sum(is.na(.)))) %>%
  gather(name, n) %>%
  group_by(name) %>%
  slice(1) %>%
  full_join(quality_vars, by = c('name' = 'value')) %>%
  ungroup %>%
  mutate(
    name = fct_relevel(name, unique(quality_vars$value)),
    value = (n/nrow(df_zscores)*100) %>% round(1),
    missing = str_c(n, ' (', value, '%)')
  ) %>%
  arrange(name) %>%
  select(key, everything())

max_plot_val <- max(df_missing$value)
p <- df_missing %>%
  ggplot(aes(x = fct_rev(key), y = value)) +
  ggalt::geom_lollipop(point.size = .5, size = .25) +
  geom_text(aes(label = str_c(value, '%', ' (', n, ')')), 
            nudge_y = max_plot_val*0.1, size = 1.5, fontface = 'bold') +
  coord_flip() +
  labs(x = 'Variable', y = 'Proportion missing (%)') +
  hrbrthemes::theme_ipsum(base_family = 'Palatino', grid = "", base_size = 6, axis_title_size = 6)

if (max_plot_val <= 0.0001) {
  p <- p + scale_y_continuous(limits = c(0, 0.1))
}
p
```

## Digit heaping charts (with mapping variable labels)
```{r digit_pref, fig.cap="Digit preference for weight \\& height measurements" %>% caption('c', .), fig.pos='!htbp', fig.fullwidth = TRUE, fig.height=3, dpi=600}
inc_progress()
# Digit preference for weight and height
digit_preference <-
  df_zscores %>%
  select(!!list_map_vars[['weight']](), !!list_map_vars[['lenhei']]()) %>%
  mutate_all(round, digits = 1) %>%
  mutate_all(funs(as.character)) %>%
  mutate_all(funs(ifelse(str_detect(., '\\.') %in% FALSE, paste0(., '.0'), .))) %>%
  mutate_all(str_extract, pattern = "\\..*") %>%
  mutate_all(funs(ifelse(is.na(.), NA_character_, paste0("0", .)))) %>%
  gather() %>%
  mutate(key = fct_inorder(key)) %>%
  group_by(key, value) %>%
  tally %>%
  group_by(key) %>%
  filter(!is.na(value)) %>%
  mutate(prop = (n/sum(n)*100) %>% round(1))

digit_preference$pretty_key <-
  factor(digit_preference$key, labels = c('Weight (kg)', 'Length or height (cm)'))

digit_preference %>%
  ggplot(aes(x = value %>% fct_rev, y = prop)) +
  ggalt::geom_lollipop(point.size = .5, size = .25) +
  coord_flip() +
  geom_text(aes(label = str_c(prop, '%')), 
            nudge_y = max(digit_preference$prop)*0.05, size = 1.5, fontface = 'bold') +
  facet_wrap(~ pretty_key, nrow = 2) +
  labs(x = 'Digit', y = 'Proportion (%)') +
  hrbrthemes::theme_ipsum(
    base_family = 'Palatino', grid = "", base_size = 7, axis_title_size = 7, axis_text_size = 5, strip_text_size = 5
  ) +
  theme(
    panel.spacing.x = unit(.04, 'cm'),
    panel.spacing.y = unit(.02, 'cm')
  )
```

\clearpage

## Z-score distribution issues
```{r zscore_density_age, fig.pos='!htbp', fig.fullwidth = T, fig.height = 4.5, fig.cap='Z-score distributions by age group' %>% caption('d', .), dpi=600}
# Z-score density plots
df_zscore_dist <-
  df_zscores %>%
  select(one_of(df_strat$value), one_of(flag_available)-1) %>%
  mutate_at(df_strat$value, funs(as.factor(.))) %>%
  gather(key, value, -tidyselect::one_of(df_strat$value)) %>%
  filter(!is.na(value)) %>% 
  mutate(key = fct_relevel(key, 'zlen', 'zwfl', 'zwei', 'zbmi')) %>%
  mutate(key = fct_recode(key, `Length- or height-for-age` = 'zlen', `Weight-for-length or height` = 'zwfl', `Weight-for-age` = 'zwei', `Body mass index-for-age` = 'zbmi'))

indx <- df_zscore_dist %>% names() %>% match(df_strat$value, nomatch = 0)
df_zscore_dist %<>% rename_at(names(.)[indx != 0], ~ df_strat$key[indx])

if(!is.null(df_zscore_dist$Sex)) {
  df_zscore_dist <- 
    df_zscore_dist %>% 
    mutate(
      Sex = recode_sex_factor(Sex)
    )
}

if(!is.null(df_zscore_dist[["Wealth quintile"]])) {
  df_zscore_dist <- 
    df_zscore_dist %>% 
    mutate(
      `Wealth quintile` = recode_wiq_factor(`Wealth quintile`)
    )
}

# we do not show NA values in the stratification variable
# similiar to the plot in the tool
df_zscore_dist_age <- dplyr::filter(
  df_zscore_dist,
  !is.na(`Age group`)
)

p <- 
  ggplot(df_zscore_dist_age) +
  stat_density(aes(value, linetype = "Samples"), size = .25, geom = "line", position = "identity") +
  anthro_ggplot2_standard_normal(linetype_as_aes = TRUE) +
  facet_grid(`Age group` ~ key) +
  xlim(-6, 6) +
  labs(x = 'z-scores', y = 'Density') +
  anthro_ggplot2_standard_normal_caption() +
  hrbrthemes::theme_ipsum(
    base_family = 'Palatino', 
    grid = "", base_size = 6, caption_size = 3, axis_title_size = 6, strip_text_size = 5, axis_text_size = 4
  ) +
  theme(
    panel.spacing.x = unit(.04, 'cm'),
    panel.spacing.y = unit(.02, 'cm')
  ) +
  theme(legend.position = "bottom") +
  anthro_scale_linetype_manual_no_groups

p
```

\clearpage

```{r zscore_density_sex, fig.pos='!htbp', fig.fullwidth = T, fig.cap='Z-score distributions by sex' %>% caption('e', .), dpi=600}
inc_progress()
p <-
  ggplot(df_zscore_dist) +
  stat_density(aes_string('value', linetype = 'Sex'), size = .25, geom = "line", position = "identity") +
  anthro_ggplot2_standard_normal() +
  facet_wrap(~ key, scales = 'free') +
  xlim(-6, 6) +
  labs(x = 'z-scores', y = 'Density', colour = df_strat$key[df_strat$value == 'Sex']) +
  anthro_ggplot2_standard_normal_caption() +
  hrbrthemes::theme_ipsum(
    base_family = 'Palatino', 
    grid = "", base_size = 6, caption_size = 3, axis_title_size = 6, strip_text_size = 5, axis_text_size = 4
  ) +
  theme(
    legend.key = element_blank(),
    legend.key.size = unit(.2, 'cm'), 
    panel.spacing.x = unit(.04, 'cm'),
    panel.spacing.y = unit(.02, 'cm')
  )

p
```

\clearpage

```{r zscore_density_gregion, fig.pos='!htbp', fig.fullwidth = T, fig.height = 4.5, fig.cap='Z-score distributions by geographical region' %>% caption('f', .), dpi=600}
inc_progress()
if(!is.null(df_zscore_dist[["Geographical region"]])) {

  ggplot(df_zscore_dist) +
    stat_density(aes(value, linetype = "Samples"), size = .25, geom = "line", position = "identity") +
    anthro_ggplot2_standard_normal(linetype_as_aes = TRUE) +
    facet_grid(`Geographical region` ~ key) +
    xlim(-6, 6) +
    labs(x = 'z-scores', y = 'Density') +
    hrbrthemes::theme_ipsum(
      base_family = 'Palatino', 
      grid = "", base_size = 6, caption_size = 3, axis_title_size = 6, strip_text_size = 5, axis_text_size = 4
    ) +
    theme(
      panel.spacing.x = unit(.04, 'cm'),
      panel.spacing.y = unit(.02, 'cm')
    ) +
    theme(legend.position = "bottom") +
    anthro_scale_linetype_manual_no_groups
}

```

\clearpage
```{r zscore_violin, results=FALSE}
inc_progress()
# Z-score box/violin plots
violin_groups <- 
  df_strat %>% 
  filter(key %in% c('Age group', 'Sex', 'Residence type', 'Wealth quintile')) %>% 
  pull(key)

ps <-
  map(violin_groups, as.name) %>%
  map(function(strat_var) {
    strat_var_chr <- as.character(strat_var)
    if (strat_var_chr == 'Wealth quintile') {
      df_zscore_dist[[strat_var_chr]] <- recode_wiq_factor(df_zscore_dist[[strat_var_chr]])
    }
    ggplot(df_zscore_dist) +
      aes(fct_rev(key), value, fill = !!strat_var) +
      geom_violin(
        size = .25, position = position_dodge(width = .9)
      ) +
      coord_flip() +
      scale_fill_grey(start = .6, end = .9, na.value = "darkred") +
      ylim(-6, 6) +
      labs(x = "Z-score measure", y = "Z-score", colour = df_strat$key[df_strat$value == .]) +
      hrbrthemes::theme_ipsum(
        base_family = "Palatino",
        grid = "", base_size = 6, axis_title_size = 6, strip_text_size = 5, axis_text_size = 4
      ) +
      theme(
        legend.key = element_blank(),
        legend.key.size = unit(.2, "cm")
      )
  })
```

```{r zscore_violin_age, fig.pos='!htbp', fig.fullwidth = TRUE, fig.height = 2.5, fig.cap=caption('g', 'z-score distribution violin plot by age group'), dpi=600}
print(ps[[1]])
```

```{r zscore_violin_sex, fig.pos='!htbp', fig.fullwidth = TRUE, fig.height = 2.5, fig.cap=caption('h', 'z-score distribution violin plot by sex'), dpi=600}
print(ps[[2]])
```

```{r zscore_violin_area, fig.pos='!htbp', fig.fullwidth = TRUE, fig.height = 2.5, fig.cap=caption('i', 'z-score distribution violin plot by residence type'), dpi=600}
is_in_group <- 'Residence type' == violin_groups
if (any(is_in_group)) {
  print(ps[[which(is_in_group)]])
}
```

```{r zscore_violin_wiq, fig.pos='!htbp', fig.fullwidth = TRUE, fig.height = 2.5, fig.cap=caption('j', 'z-score distribution violin plots by wealth quintile'), dpi=600}
is_in_group <- 'Wealth quintile' == violin_groups
if (any(is_in_group)) {
  print(ps[[which(is_in_group)]])
}
```

\clearpage

# Appendix: Nutritional status tables

\footnotesize
```{r}
inc_progress()

to_NA <- function(x, y) {
  y[is.na(x) | x == "NA"] <- NA_character_
  y
}
f_num <- function(x, digits = 1) format(as.numeric(x), nsmall = digits)

additional_oedema_col <- if (is_oedema_mapped) {
  "Oedema_cases"
} else {
  NULL
}

# just in case the Oedema_cases column was not generated
if (is_oedema_mapped && is.null(df_prevs[[additional_oedema_col]])) {
  additional_oedema_col <- NULL
}

list_zscore <-
  c('HA', 'WA') %>% 
  map(function(x) {
    df_prevs %>%
      select(Group, starts_with(x), -matches('_se|[A-Z][0-9]|1_|_W'), !!! additional_oedema_col) %>%
      mutate_at(
        .vars = vars(matches('_pop|_r|_ll|_ul')), 
        .funs = funs(as.numeric(.) %>% round(1))
      ) %>% 
      filter(!str_detect(Group, 'age_sex')) %>%
      set_names(c('disaggregation', 'weighted', 'unweighted', 'r_3', 'll_3', 'ul_3', 'r_2', 'll_2', 'ul_2', 'r', 'll', 'ul', 'sd', additional_oedema_col)) %>%
      mutate_at(
        .vars = vars(weighted:ul), 
        .funs = funs(round(as.numeric(.), 1))
      ) %>%
      mutate(unweighted = as.integer(unweighted),
             sd = round(sd, 2)) %>% 
      mutate(
        `-3` = to_NA(weighted, str_c(f_num(r_3), ' (', f_num(ll_3), '; ', f_num(ul_3), ')')),
        `-2` = to_NA(weighted, str_c(f_num(r_2), ' (', f_num(ll_2), '; ', f_num(ul_2), ')')),
        mean = to_NA(weighted, str_c(f_num(r), ' (', f_num(ll), '; ', f_num(ul), ')'))
      ) %>%
      select(-matches('^r|^ll|^ul')) %>%
      mutate_at(.vars = vars(weighted:unweighted), .funs = funs(as.numeric)) %>% 
      mutate_at(.vars = vars(disaggregation), .funs = funs(str_trim)) %>% 
      set_names(
        c(
          'Group', 'Weighted N', 'Unweighted N', 'z-score SD', additional_oedema_col,
          '-3SD (95% CI)', '-2SD (95% CI)', 
          'z-score mean (95% CI)'
        )
      ) %>% 
      select(1:3, !!(if (is_oedema_mapped) 6:7 else 5:7), 4, !! (if (is_oedema_mapped) 5 else NULL))
  }) %>%
  set_names(c('Stunting (Height-for-age)', 'Weight-for-age'))

weight_for_height <-
  df_prevs %>%
  select(
    Group,
    starts_with('WH'),
    -matches('_se|1_|_W'),
    !!! additional_oedema_col
  ) %>%
  filter(!str_detect(Group, 'age_sex')) %>%
  set_names(
    c(
      'disaggregation', 'weighted', 'unweighted',
      'r_3', 'll_3', 'ul_3',
      'r_2', 'll_2', 'ul_2',
      'r2', 'll2', 'ul2',
      'r3', 'll3', 'ul3',
      'r', 'll', 'ul', 'sd', additional_oedema_col
    )
  ) %>%
  mutate_at(
    .vars = vars(weighted:ul), 
    .funs = funs(round(as.numeric(.), 1))
  ) %>%
  mutate(unweighted = as.integer(unweighted),
       sd = round(sd, 2)) %>% 
  mutate(
    `-3` = to_NA(weighted, str_c(f_num(r_3), ' (', f_num(ll_3), '; ', f_num(ul_3), ')')),
    `-2` = to_NA(weighted, str_c(f_num(r_2), ' (', f_num(ll_2), '; ', f_num(ul_2), ')')),
    `+2` = to_NA(weighted, str_c(f_num(r2), ' (', f_num(ll2), '; ', f_num(ul2), ')')),
    `+3` = to_NA(weighted, str_c(f_num(r3), ' (', f_num(ll3), '; ', f_num(ul3), ')')),
    mean = to_NA(weighted, str_c(f_num(r), ' (', f_num(ll), '; ', f_num(ul), ')'))
  ) %>%
  mutate_at(.vars = vars(weighted:unweighted), .funs = funs(as.numeric)) %>% 
  mutate_at(.vars = vars(disaggregation), .funs = funs(str_trim)) %>% 
  select(-matches('^r|^ll|^ul')) %>%
  set_names(
    c(
      'Group', 'Weighted N', 'Unweighted N', 'z-score SD', additional_oedema_col,
      '-3SD (95% CI)', '-2SD (95% CI)',
      '+2SD (95% CI)', '+3SD (95% CI)', 
      'z-score mean (95% CI)'
    )
  ) %>%
  select(1:3, !!(if (is_oedema_mapped) 6:9 else 5:9), 4, !! (if (is_oedema_mapped) 5 else NULL)) %>%
  list %>%
  set_names('Weight-for-height')

list_zscore %<>% c(weight_for_height)

# remove the Oedema_cases column for height for age if oedema is mapped
# as the oedema information is only relevant for Weight-for-age and Weight-for-height
if (is_oedema_mapped && !is.null(list_zscore[[1]][["Oedema_cases"]])) {
  list_zscore[[1]][["Oedema_cases"]] <- NULL
}
cat('\n')
knitr::kable(list_zscore[[1]], caption = 'Height-for-age',booktabs = TRUE, align = c('l', 'r', rep('r', ncol(list_zscore[[1]])-1)))

cat('\\clearpage')
cat('\n')
knitr::kable(list_zscore[[2]], caption = 'Weight-for-age', booktabs = TRUE, align = c('l', 'r', rep('r', ncol(list_zscore[[2]])-1)))
print_oedema_note(oedema_n)

cat('\\clearpage')
cat('\n')
knitr::kable(list_zscore[[3]], caption = 'Weight-for-height', booktabs = TRUE, align = c('l', 'r', rep('r', ncol(list_zscore[[3]])-1)))
print_oedema_note(oedema_n)
```
